A quantum parallel Markov chain Monte Carlo

### 2022-02-28 main.tex
updated figure warm start mcmc

% !TeX document-id = {d42653b9-9ea4-48c2-860b-3d6e6e9d8ab0}
% !TeX TXS-program:compile = txs:///pdflatex/[--shell-escape]
\documentclass[12pt]{article} % For LaTeX2e
%\usepackage{neurips_2021}
\usepackage[colorlinks, citecolor={blue}]{hyperref}
\usepackage{url}
\usepackage{amsfonts,amscd,amssymb}
\usepackage{amsthm,amsmath,natbib}
\usepackage{mathtools}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\usepackage{algorithm2e}
\usepackage{bm}
\usepackage{bbm} %bb font numbers
\usepackage[table]{xcolor}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{natbib}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
%\usepackage[nolists]{endfloat}
\usepackage{listings}
\usepackage[textsize=tiny]{todonotes}
\usepackage{tikz}
\usetikzlibrary{shapes.misc}
\usepackage{etoolbox}
\usepackage{appendix}
\usepackage[format=plain,
labelfont={it},
textfont=it]{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{xr}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{authblk}
\usepackage{mathbbol}
\usepackage{braket}
\usepackage{minted}

@@

 \begin{figure}[!t]
 	\vspace{3em}
	\centering
	\includegraphics[width=0.9\linewidth]{mcmcIterations.pdf}
	\caption{Total number of oracle evaluations required for each of 2,000 parallel MCMC iterations. In total, the combined MCMC runs required roughly $7$\% of the usual 20 million target evaluations. Over  99.4\% of the 10,000 MCMC iterations successfully sampled from the discrete distribution with probabilities of Equation \eqref{eq:probs}.}\label{fig:mcmcIterations}
\end{figure}

>>>>

% !TeX document-id = {d42653b9-9ea4-48c2-860b-3d6e6e9d8ab0}
% !TeX TXS-program:compile = txs:///pdflatex/[--shell-escape]
\documentclass[12pt]{article} % For LaTeX2e
%\usepackage{neurips_2021}
\usepackage[colorlinks, citecolor={blue}]{hyperref}
\usepackage{url}
\usepackage{amsfonts,amscd,amssymb}
\usepackage{amsthm,amsmath,natbib}
\usepackage{mathtools}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\usepackage{algorithm2e}
\usepackage{bm}
\usepackage{bbm} %bb font numbers
\usepackage[table]{xcolor}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{natbib}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
%\usepackage[nolists]{endfloat}
\usepackage{listings}
\usepackage[textsize=tiny]{todonotes}
\usepackage{tikz}
\usetikzlibrary{shapes.misc}
\usepackage{etoolbox}
\usepackage{appendix}
\usepackage[format=plain,
labelfont={it},
textfont=it]{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{xr}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{authblk}
\usepackage{mathbbol}
\usepackage{braket}
\usepackage[cache=false]{minted}

@@

 \begin{figure}[!t]
 	\vspace{3em}
	\centering
	\includegraphics[width=0.9\linewidth]{mcmcIterations.pdf}
	\caption{Total number of oracle evaluations required for each of 2,000 parallel MCMC iterations. In total, the combined MCMC runs required roughly $7$\% of the usual 20 million target evaluations. Over  99.4\% of the 10,000 MCMC iterations successfully sampled from the discrete distribution with probabilities of Equation \eqref{eq:probs}. Burn-in evaluations require moderately more evaluations because the current state occupies a lower density region and represents a `less good' warm-start.}\label{fig:mcmcIterations}
\end{figure}
